Code to reproduce results in _Semi-parametric generalized linear model for

### 2022-03-11 ManuscriptCode/Manuscript.Rmd
Change BB to binomial for "both correct" setting

  1. Both the beta-binomial and semi-parameteric model are correct - a binomial backbone, which belongs to the exponential family
  2. Only the beta-binomial model is correct - generated from a beta-binomial distribution
  3. Only the semi-parametric model is correct - generated from the spglm, with a q-power backbone
  4. Neither model is correct - generated from a q-power distribution
 * fit the data using our semi-parametric regression model, beta-binomial regression (potentially misspecified distribution), and GEE (marginal only)

@@

```{r AnalyzeOne}
run_analysis <- function(dat, cs_predict=5){
  #GEE
  dat_long <- unwrap(dat)
  res_gee <- geeglm(Resp ~ X1 + X2, data=dat_long, id = ID, family=binomial,
                 corstr = "exch")
  #Beta-binomial
  res_bb <- vgam(cbind(NResp, ClusterSize - NResp) ~  X1 + X2, weights = Freq,
                 data=dat, family =  betabinomial(lmu="logitlink"))
  #SPGLM
  op <- options(warn=-1)
  res_spglm <- spglm(cbind(NResp, ClusterSize - NResp) ~ X1 + X2, data=dat,
                   weights  = Freq)
  options(op)

  # predict PDF at cluster-size cs_predict & all covariates = 0
  newd <- data.frame(X1 = 0, X2 = 0)
  # beta-binomial
  mns_rho <- predictvglm(res_bb, type="link", newdata=newd, untransform=TRUE)

  fit_bb <- newd %>% 
    crossing(NResp=0:cs_predict) %>%
    mutate(ClusterSize = cs_predict,
           Prob = dbetabinom(NResp, size=cs_predict, prob=mns_rho[1,"mu"], rho=mns_rho[1,"rho"])) %>%
  mutate(Model="BB")

@@

  nms <- names(coef(res_spglm))
  res <- bind_rows(
    GEE = tibble(Term = nms, 
                 Est=coef(res_gee), 
                 SE = sqrt(diag(vcov(res_gee)))),
    BB = tibble(Term = nms,
                Est = coef(res_bb)[-2],      # second value is logit(rho)   
                SE=sqrt(diag(vcov(res_bb)))[-2]),
    SPGLM = tibble(Term = nms,
                   Est = coef(res_spglm), 
                   SE= sqrt(diag(vcov(res_spglm)))),
    .id = "Model")

  fit <- bind_rows(fit_bb, fit_spglm) %>%
    mutate(Type = "PDF")

@@

```{r ActualSim1, warning=FALSE}
R <- 100
cs_predict <- 5
p_predict <- 1/(1+exp(-c(beta_correct %*% c(0,0,0))))

# Scenario 1: binomial PDF
sim1 <- 
  replicate(R,
            {simd <- sim_covariates(100) %>% 
                add_response_param(rfun=function(n, cs, p)rbinom(n, size=cs, prob=p));
             run_analysis(simd, cs_predict = cs_predict)}, 
            simplify = FALSE)  %>%
   bind_rows(.id="ID")

@@

```{r Compare}
comb <- bind_rows(`Both correct` = sim1, 
                  `BB correct`= sim2,
                  `SPGLM correct` = sim3, 
                  `Neither correct` = sim4,
                  .id="Generator") %>%
  mutate(Generator= factor(Generator, levels = c("Both correct",
                                                 "BB correct",
                                                 "SPGLM correct",
                                                 "Neither correct")),
         Model = factor(Model, levels = c("BB","SPGLM","GEE")))

# get correct values of parameters 
correct_beta <- tibble(Term = c("(Intercept)","X1","X2"),
                  Correct = beta_correct)
correct_pdf <- bind_rows(`Both correct` = pdf1, 
                         `BB correct`= pdf2,
                         `SPGLM correct` = pdf3, 
                         `Neither correct` = pdf4,
                         .id="Generator") %>%
  mutate(Term = as.character(NResp),
         Generator= factor(Generator, levels = c("Both correct",
                                                 "BB correct",
                                                 "SPGLM correct",
                                                 "Neither correct")))

@@

scomb <- comb_beta %>%
  group_by(Generator, Term, Model) %>%
  summarize(bias = mean(Est-Correct, na.rm=TRUE),
            mc.se = sd(Est, na.rm=TRUE),
            se = mean(SE, na.rm=TRUE),
            .groups="drop_last") %>%
  mutate(rel.eff = mc.se / mc.se[Model=="GEE"]) %>%
  ungroup() %>%
  arrange(Generator, Model, Term)
kable(scomb, digits=3)
```

@@

>>>>

  1. Both the parametric (binomial) and semi-parameteric model are correct - a binomial backbone, which belongs to the exponential family
  2. Only the parametric (beta-binomial) model is correct - generated from a beta-binomial distribution
  3. Only the semi-parametric model is correct - generated from the spglm, with a q-power backbone
  4. Neither model is correct - generated from a q-power distribution
 * fit the data using our semi-parametric regression model, beta-binomial regression (potentially misspecified distribution), and GEE (marginal only)

@@

```{r AnalyzeOne}
run_analysis <- function(dat, cs_predict=5, Binom = FALSE){
  #GEE
  dat_long <- unwrap(dat)
  res_gee <- geeglm(Resp ~ X1 + X2, data=dat_long, id = ID, family=binomial,
                 corstr = "exch")

  if (Binom){
    #Binomial
    res_bin <- glm(cbind(NResp, ClusterSize - NResp) ~  X1 + X2, weights = Freq,
                  data=dat, family =  binomial)
  } else {
    #Beta-binomial
    res_bb <- vgam(cbind(NResp, ClusterSize - NResp) ~  X1 + X2, weights = Freq,
                 data=dat, family =  betabinomial(lmu="logitlink"))
  }

  #SPGLM
  op <- options(warn=-1)
  res_spglm <- spglm(cbind(NResp, ClusterSize - NResp) ~ X1 + X2, data=dat,
                   weights  = Freq)
  options(op)

  # predict PDF at cluster-size cs_predict & all covariates = 0
  newd <- data.frame(X1 = 0, X2 = 0)
  nms <- names(coef(res_spglm))

  if (Binom){   
    # binomial
    mns <- predict(res_bin, type="response", newdata=newd)

   fit_binbb <- newd %>% 
      crossing(NResp=0:cs_predict) %>%
      mutate(ClusterSize = cs_predict,
            Prob = dbinom(NResp, size=cs_predict, prob=mns)) %>%
    mutate(Model="Binom/BB")

   ests_binbb <- tibble(Term = nms,
                 Est = coef(res_bin),
                 SE = sqrt(diag(vcov(res_bin))))
  } else {
    # beta-binomial
    mns_rho <- predictvglm(res_bb, type="link", newdata=newd, untransform=TRUE)

    fit_binbb <- newd %>% 
      crossing(NResp=0:cs_predict) %>%
      mutate(ClusterSize = cs_predict,
            Prob = dbetabinom(NResp, size=cs_predict, prob=mns_rho[1,"mu"],
                              rho=mns_rho[1,"rho"])) %>%
    mutate(Model="Binom/BB")

    ests_binbb <- tibble(Term = nms,
                Est = coef(res_bb)[-2],      # second value is logit(rho)   
                SE=sqrt(diag(vcov(res_bb)))[-2])
  }

@@

  res <- bind_rows(
    GEE = tibble(Term = nms, 
                 Est=coef(res_gee), 
                 SE = sqrt(diag(vcov(res_gee)))),
    `Binom/BB` = ests_binbb,
    SPGLM = tibble(Term = nms,
                   Est = coef(res_spglm), 
                   SE= sqrt(diag(vcov(res_spglm)))),
    .id = "Model")

  fit <- bind_rows(fit_binbb, fit_spglm) %>%
    mutate(Type = "PDF")

@@

```{r ActualSim1, warning=FALSE}
R <- 500
cs_predict <- 5
p_predict <- 1/(1+exp(-c(beta_correct %*% c(0,0,0))))

# Scenario 1: binomial PDF
sim1 <- 
  replicate(R,
            {simd <- sim_covariates(100) %>% 
                add_response_param(rfun=function(n, cs, p)rbinom(n, size=cs, prob=p));
             run_analysis(simd, cs_predict = cs_predict, Binom = TRUE)}, 
            simplify = FALSE)  %>%
   bind_rows(.id="ID")

@@

```{r Compare}
comb <- bind_rows(`Both correct` = sim1, 
                  `Parametric correct`= sim2,
                  `SPGLM correct` = sim3, 
                  `Neither correct` = sim4,
                  .id="Generator") %>%
  mutate(Generator= factor(Generator, levels = c("Both correct",
                                                 "Parametric correct",
                                                 "SPGLM correct",
                                                 "Neither correct")),
         Model = factor(Model, levels = c("Binom/BB","SPGLM","GEE")))

# get correct values of parameters 
correct_beta <- tibble(Term = c("(Intercept)","X1","X2"),
                  Correct = beta_correct)
correct_pdf <- bind_rows(`Both correct` = pdf1, 
                         `Parametric correct`= pdf2,
                         `SPGLM correct` = pdf3, 
                         `Neither correct` = pdf4,
                         .id="Generator") %>%
  mutate(Term = as.character(NResp),
         Generator= factor(Generator, levels = c("Both correct",
                                                 "Parametric correct",
                                                 "SPGLM correct",
                                                 "Neither correct")))

@@

scomb <- comb_beta %>%
  group_by(Generator, Term, Model) %>%
  summarize(bias = mean(Est-Correct, na.rm=TRUE),
            mc.se = sd(Est, na.rm=TRUE),
            se = mean(SE, na.rm=TRUE),
            .groups="drop_last") %>%
  mutate(rel.eff = mc.se / mc.se[Model=="GEE"],
         se.rel.bias = mc.se/se) %>%
  ungroup() %>%
  arrange(Generator, Model, Term)
kable(scomb, digits=3)
```

@@

ggplot(comb_pdf, aes(x=NResp, y=Est-Correct, fill=Model, outlier.fill=Model)) +
  facet_wrap(~Generator) +
  geom_hline(yintercept = 0, colour="black", size=1) +
  stat_summary(aes(color=Model), fun=mean, geom="line") +
  geom_boxplot(aes(group=interaction(Model, NResp)), 
               position=position_dodge(width=0.6), width=0.5, 
               outlier.size =1, outlier.alpha=0.5) +
  scale_y_continuous("Bias of probability") +
  scale_x_continuous("# of responses", breaks = 0:cs_predict) +
  scale_fill_manual(breaks=names(cols), values=cols)
